### 2020-11-11 cv/cv-body.tex
Update CV

@@

N.Z. Janjua, D. Coombs, C. Colijn. Estimating the impact of COVID-19

@@

at PLOS Computational Biology. Preprint: medRxiv 2020.04.17.20070086.

@@

Cahill, C.L., \textbf{S.C. Anderson}, A.J. Paul, L. MacPherson, M.G.
Sullivan, B.T. van Poorten, C.J. Walters, and J.R. Post. A
spatial-temporal approach to modeling somatic growth across inland
recreational fisheries landscapes. In press at Canadian Journal of
Fisheries and Aquatic Sciences.
\url{https://doi.org/10.1139/cjfas-2019-0434}.

@@

Litzow, M.A., M.E. Hunsicker, E.J. Ward, \textbf{S.C. Anderson}, J. Gao,
S. Zador, S. Batten, S. Dressel, J. Duffy-Anderson, E. Fergusson, R.
Hopcroft, B.J. Laurel, and R. O'Malley. Evaluating ecosystem change as
Gulf of Alaska temperature exceeds the limits of preindustrial
variability. Progress in Oceanography. 186:102393.
\url{https://doi.org/10.1016/j.pocean.2020.102393}.

@@

transparency, assessment efficiency, and monitoring. In press at
Fisheries. \url{https://doi.org/10.1002/fsh.10441}.

>>>>

\textbf{Anderson, S.C.}, P.R. Elsen, B.B. Hughes, R.K. Tonietto, M.C.
Bletz, D.A. Gill, M.A.\ Holgerson, S.E. Kuebbing, C. McDonough MacKenzie,
M.H. Meek, D. Veríssimo. Trends in ecology and conservation over eight
decades. In press at Frontiers in Ecology and the Environment.

@@

N.Z. Janjua, D. Coombs, C. Colijn. Quantifying the impact of COVID-19

@@

at PLOS Computational Biology. medRxiv preprint:

@@

Maureaud, A., R. Frelat, L. Pecuchet, N.L. Shackell, B. Merigot, M.L.
Pinsky, K. Amador, \textbf{S.C. Anderson}, \ldots{} (67 co-authors),
J.T. Thorson. Are we ready to track climate-driven shifts in marine
species across international boundaries? A global survey of scientific
bottom trawl data. In press at Global Change Biology.
\url{https://doi.org/10.1111/gcb.15404}.

@@

Cahill, C.L., \textbf{S.C. Anderson}, A.J. Paul. L. Macphearson, M.G.
Sullivan, B. van Poorten, C. Walters, J.R. Post. A spatial-temporal
approach to modeling somatic growth across recreational fisheries
landscapes. Canadian Journal of Fisheries and Aquatic Science.
77(11):1822--1835. \url{https://doi.org/10.1139/cjfas-2019-0434}.
Litzow, M.A., M.E. Hunsicker, E.J. Ward, \textbf{S.C. Anderson}, J. Gao
, S. Zador, S. Batten , S. Dressel, J. Duffy-Anderson, E. Fergusson, R.
Hopcroft, B.J. Laurel, R. O'Malley Evaluating ecosystem change as Gulf
of Alaska temperature exceeds the limits of preindustrial variability.
Progress in Oceanography. 186:102393.
\url{https://doi.org/10.1016/j.pocean.2020.102393}

@@

transparency, assessment efficiency, and monitoringy. Fisheries.
45:535--543. \url{https://doi.org/10.1002/fsh.10441}.
(\href{https://www.dropbox.com/s/y8b0rlxvnodngf8/Anderson_etal_2020_reproducible_visualization.pdf?dl=1}{PDF})
